An Example Article

### 2023-04-25 amsart-en/amsart-temp.tex
update

% blankbox for figure
\newcommand{\blankbox}[2]{%
\parbox{\columnwidth}{\centering
\setlength{\fboxsep}{0pt}%
\fbox{\raisebox{0pt}[#2]{\hspace{#1}}}}%
}

@@

\author[Author A \; \& \; Author B]{Author A${\,}^{1}$ \quad and \quad Author B${\,}^{2,*}$}

\thanks{${}^{*}$ Corresponding author (E-mail: \texttt{xyz@math.univ.edu}). \\
\indent ${}^{1}$ Department of Computer Science, \LaTeX\ University. \\
\indent ${}^{2}$ Department of Mechanical Engineering, \LaTeX\ University \\
\indent This work is supported in part by NSFC grants No. 12345678 and ...
}

>>>>

% blank box for figure
\newcommand{\blankbox}[2]{%
  \parbox{\columnwidth}{\centering
  \setlength{\fboxsep}{0pt}%
  \fbox{\raisebox{0pt}[#2]{\hspace{#1}}}}%
}

@@

\author[Author A and Author B]{Author A${}^{1}$ and Author B${}^{2,*}$}

\thanks{${}^{*}$Corresponding author (E-mail: \texttt{xyz@math.univ.edu})}
\thanks{${}^{1}$Department of Computer Science, \LaTeX\ University}
\thanks{${}^{2}$Department of Mechanical Engineering, \LaTeX\ University}
\thanks{This work is supported in part by NSFC grants No. 12345678 and ...}

### 2023-04-25 article-en/article-temp.tex
update

\author{
  Author A\thanks{Department of Computer Science, \LaTeX\ University.}
  \and
  Author B\thanks{Department of Mathematics, \LaTeX\ University.}
  %\thanks{Email address: \texttt{xyz@math.univ.edu}}
  \and
  Author C\thanks{Department of Mechanical Engineering, \LaTeX\ University}
}

>>>>

\author{
  Author A\thanks{Department of Computer Science, \LaTeX\ University}~,
  Author B\thanks{Department of Mathematics, \LaTeX\ University}~,
  and
  Author C\thanks{Department of Mechanical Engineering, \LaTeX\ University}
}

### 2023-04-25 article-en/article-temp3.tex
update

% package for mathematics
\usepackage{amsmath,amssymb,amsthm}
% package for RSFS fonts in maths
\usepackage{mathrsfs}
% package for special symbols
\usepackage{pifont}
% package for multilingual support
\usepackage[english]{babel}
% package for figures
\usepackage{graphicx}
\usepackage{subfigure}
% package for hyperlink
\usepackage{url,hyperref}
% package for layout of list
\usepackage{enumitem}
% package for showing keys in draft mode
\usepackage[notcite,notref]{showkeys}
% package for color
\usepackage{color}
% package for table
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{makecell}
% package for multiple columns and rows
\usepackage{multirow,multicol}
% package for caption
\usepackage{caption}
% package for algorithm
\usepackage{algorithm}
\usepackage{algpseudocode}
% package for author and affiliation style
\usepackage[affil-it]{authblk}
% package for using box and verbatim
\usepackage{fancybox}

@@

% new command
\newcommand{\abs}[1]{\lvert#1\rvert}
\newcommand{\dx}[1][x]{\,{\rm d}#1}
\newcommand{\ddx}[1][x]{\dfrac{\rm d}{{\rm d}#1}}
\newcommand{\refe}[2]{(\ref{#1})--(\ref{#2})}
\newcommand{\red}[1]{\textcolor{red}{#1}}

% Information for title and author
\title{An Example Article\thanks{The work is supported in part by NSF Grant No. 12345678 and ...}}

@@

\author{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
\affil{Department of Computer Science, \LaTeX\ University.}

\author{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
\affil{Department of Mathematics, \LaTeX\ University.}

\author{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
\affil{Department of Mechanical Engineering, \LaTeX\ University}

@@

The merits of our method are as follows:
\begin{itemize}
  \item item one
  \item item two
\end{itemize}
\begin{enumerate}
  \item item one
  \item item two
\end{enumerate}

@@

LaTeX is a high-quality typesetting system; it includes features designed
for the production of technical and scientific documentation.
LaTeX is the de facto standard for the communication and publication of scientific documents.
LaTeX is based on the idea that it is better to leave document design to
document designers, and to let authors get on with writing documents.

>>>>

% package for mathematics
\usepackage{amsmath,amssymb,amsthm}
% package for RSFS fonts in maths
\usepackage{mathrsfs}
% package for special symbols
\usepackage{pifont}
% package for multilingual support
\usepackage[english]{babel}
% package for figures
\usepackage{graphicx}
\usepackage{subfigure}
% package for hyperlink
\usepackage{hyperref}
% package for layout of list
\usepackage{enumitem}
% package for showing keys in draft mode
\usepackage[notcite,notref]{showkeys}
% package for color
\usepackage{color}
% package for table
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{makecell}
% package for multiple columns and rows
\usepackage{multirow,multicol}
% package for caption
\usepackage{caption}
% package for algorithm
\usepackage{algorithm,algorithmicx}
\usepackage{algpseudocode}
% package for using box and verbatim
\usepackage{fancybox}

% package for bibliography support
\usepackage[numbers,sort&compress]{natbib}

@@

% graphic path
\graphicspath{{./figures/}}

% differential operator
\newcommand{\dif}{\mathop{}\!\mathrm{d}}

% new command
\newcommand{\abs}[1]{\lvert#1\rvert}
\newcommand{\norm}[1]{\lVert#1\rVert}
\newcommand{\dx}[1][x]{\mathop{}\!\mathrm{d}#1}
\newcommand{\ii}{\mathrm{i}\mkern1mu} % imaginary
\newcommand{\refe}[2]{(\ref{#1})--(\ref{#2})}
\newcommand{\red}[1]{\textcolor{red}{#1}}

% Information for title and author
\title{An Example Article}

@@

\author{
  Author A \\
  {\itshape Department of Computer Science, \LaTeX\ University} \\
  \and
  Author B\thanks{Email address: \texttt{xyz@math.univ.edu}} \\
  {\itshape Department of Mathematics, \LaTeX\ University} \\
  \and
  Author C\thanks{This author was supported in part by NSF Grant No. 12345678.} \\
  {\itshape Department of Mechanical Engineering, \LaTeX\ University} \\
}

@@

The merits of our method are as follows:
\begin{itemize}
  \item item one
  \item item two
  %\item item three
\end{itemize}
\begin{enumerate}
  \item item one
  \item item two
  %\item item three
\end{enumerate}

@@

%LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
%LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents.
